---
title: "Housing Prices"
author: "Mine Cetinkaya-Rundel"
toc: true
number-sections: true
highlight-style: pygments
format: 
  html: 
    code-fold: true
---

## Introduction

In this analysis, we build a model predicting sale prices of houses based on data on houses that were sold in the Duke Forest neighborhood of Durham, NC around November 2020. Let's start by loading the packages we'll use for the analysis.

```{r}
#| label: load-pkgs
#| code-summary: "Packages"
#| warning: false
#| echo: true

library(openintro)  # for data
library(tidyverse)  # for data wrangling and visualization
library(knitr)      # for tables
library(broom)      # for model summary
```

We present the results of exploratory data analysis in @sec-eda and the regression model in @sec-model.

<!--# ADD CITATION HERE -->

## Exploratory data analysis {#sec-eda}

The data contains `r nrow(duke_forest)` houses. As part of the exploratory analysis let's visualize and summarize the relationship between areas and prices of these houses.

### Data visualization

@fig-histogram shows two histograms displaying the distributions of `price` and `area` individually.

```{r}
#| label: fig-histogram
#| fig-cap: "Histograms of individual variables"
#| fig-subcap:
#|   - "Histogram of `price`s"
#|   - "Histogram of `area`s" 
#| layout-ncol: 2

ggplot(duke_forest, aes(x = price)) +
  geom_histogram(binwidth = 50000) +
  labs(title = "Histogram of prices")

ggplot(duke_forest, aes(x = area)) +
  geom_histogram(binwidth = 250) +
  labs(title = "Histogram of areas")
```

@fig-scatterplot displays the relationship between these two variables in a scatterplot.

```{r}
#| label: fig-scatterplot
#| fig-cap: "Scatterplot of price vs. area of houses in Duke Forest"

ggplot(duke_forest, aes(x = area, y = price)) +
  geom_point() +
  labs(title = "Price and area of houses in Duke Forest")
```

### Summary statistics

@tbl-stats displays basic summary statistics for these two variables.

```{r}
#| label: tbl-stats
#| tbl-cap: "Summary statistics for price and area of houses in Duke Forest"

duke_forest %>%
  summarise(
    `Median price` = median(price),
    `IQR price` = IQR(price),
    `Median area` = median(area),
    `IQR area` = IQR(area),
    `Correlation, r` = cor(price, area)
    ) %>%
  kable(digits = c(0, 0, 0, 0, 2))
```

## Modeling {#sec-model}

We can fit a simple linear regression model of the form shown in @eq-slr.

@tbl-lm shows the regression output for this model.

```{r}
#| label: tbl-lm
#| tbl-cap: "Linear regression model for predicting price from area"

price_fit <- lm(price ~ area, data = duke_forest)
  
price_fit %>%
  tidy() %>%
  kable(digits = c(0, 0, 2, 2, 2))
```

## Equations

We can add simple like this

$E = mc^{2}$

Or like this

$$E = mc^{2}$$

## Call-out

Callouts are markdown divs that have special callout attributes. To create a callout within a markdown cell, type the following in your document.

Here a callout-note:

::: callout-note
Note that there are five types of callouts, including: `note`, `tip`, `warning`, `caution`, and `important`.
:::

Here a callout_caution:

::: callout-caution
Note that there are five types of callouts, including: `note`, `tip`, `warning`, `caution`, and `important`.
:::

<!--# ADD CALLOUT HERE -->

<!--# ADD SECTION HEADING FOR REFERENCES HERE -->
